Draft Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-04-24 draftfinalreport_v3.Rnw
update figures in 4.3 for MMR2 date etc.

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{vacc_age.pdf}
\end{center}
\caption{Age of vaccination of vaccinated measles cases, 2007- 12 June 2014. Recommended vaccination age in months is shown for the measles, mumps, rubella (MMR) dose 1 (12 months) and MMR dose 2 (60 months)}
\label{fig:vaccstat}
\end{figure}

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{dob_vacc_unvac.pdf}
\end{center}
\caption{Year of birth of unvaccinated of measles cases, 2007- 12 June 2014}
\label{fig:yearandvac}
\end{figure}

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{dob_vacc_dose.pdf}
\end{center}
\caption{Year of birth of unvaccinated of measles cases, 2007- 12 June 2014. The year of birth for those vaccinated with measles, mumps, and rubella (MMR) dose 1 is shown in the upper panel, MMR dose 2 the lower panel.}
\label{fig:yearandvacf}
\end{figure}

>>>>

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{vacc_age.pdf}
\end{center}
\caption{Age of vaccination of vaccinated measles cases, 2007--12~June~2014. Recommended vaccination age in months is shown for the measles, mumps, rubella (MMR) dose 1 (12 months) and MMR dose 2 (4 years)}
\label{fig:vaccstat}
\end{figure}

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{dob_vacc_unvac.pdf}
\end{center}
\caption{Year of birth of unvaccinated of measles cases, 2007--12~June~2014}
\label{fig:yearandvac}
\end{figure}

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{dob_vacc_dose.pdf}
\end{center}
\caption{The year of birth for those vaccinated with measles, mumps, and rubella (MMR) dose 1 is shown in the upper panel, MMR dose 2 the lower panel.}
\label{fig:yearandvacf}
\end{figure}
